Formalization of Network Flow Algorithms

### 2017-03-01 paper/root.tex

@@

\begin{figure}[!h]    
  \begin{tikzpicture}[thick,scale=.8, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{groupplot}[
        group style={
            group size=2 by 3,
            vertical sep=1.5cm,
        }
    ]

    \nextgroupplot[
        title={Random Sparse Graphs},
        title style={yshift=-2ex},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1k$, $2k$, $3k$, $4k$, $5k$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$},
        smooth,
        cycle list name = black white,
        legend cell align={left},
        legend to name=grouplegend
    ]
    % legend information
      \addlegendimage{fill=gray, mark=square}
      \addlegendimage{fill=gray, mark=square*}
      \addlegendimage{fill=gray, mark=*}
      \addlegendimage{fill=gray, mark=o}
      \addlegendimage{fill=gray, mark=otimes*}
      \addlegendentry{Edmonds-Karp, SML}
      \addlegendentry{FIFO push-relabel, SML}
      \addlegendentry{Edmonds-Karp, Java}
      \addlegendentry{FIFO push-relabel, C++}
      \addlegendentry{FIFO push-relabel, C}
    % end legend information

@@

		  \addplot+[mark=*] table {
		    1000 .024   
		    1500 .054   
		    2000 .103  
		    2500 .399  
		    3000 .719  
		    3500 1.362 
		    4000 2.036 
		    4500 3.334 
		    5000 4.785 
		    5500 6.079     
		  }; %Sparse, Edka, Java

@@

		  \addplot+[mark=*] table {
		    1000	3.982
		    1050	4.463
		    1100	5.278
		    1150	6.27
		    1200	6.939
		    1250	7.953
		    1300	9.392
		    1350	10.317
		    1400	14.71
		    1450	13.11  
		  }; %Dense, Edka, Java

@@

    \node at (group c1r3.east) [anchor=west, xshift= 1cm] {\ref{grouplegend}};
  \end{tikzpicture}
\caption{Benchmark of different implementations. The x-axis shows the number of nodes, the y axis the execution time in seconds.}\label{fig:benchmark}
\end{figure}

>>>>

\usepgfplotslibrary{groupplots}

@@

\begin{figure}[!h]
\begin{center}    
  \begin{tikzpicture}[thick,scale=.75, every node/.style={scale=1}] %change the scales if you like to reduce the size
    \begin{groupplot}[
        group style={
            group size=2 by 3,
            vertical sep=1.4cm,
        }
    ]

    \nextgroupplot[
        title={Random Sparse Graphs},
        title style={yshift=-2ex},
        axis x line*= bottom,
        axis y line*= left,
        xmode = log,
        ymode = log,
        xtick = {0,1000,...,5000},
        ytick = {0.01,0.1,1,10},
        xticklabels = {$1k$, $2k$, $3k$, $4k$, $5k$},
        yticklabels = {$0.01$,$0.1$,$1$,$10$},
        smooth,
        cycle list name = black white,
        legend cell align={left},
        legend to name=grouplegend
    ]
    % legend information
      \addlegendimage{fill=gray, mark=square}
      \addlegendimage{fill=gray, mark=square*}
      \addlegendimage{dashed, every mark/.append style={solid, fill=gray}, mark=*}
      \addlegendimage{fill=gray, mark=o}
      \addlegendimage{fill=gray, mark=otimes*}
      \addlegendentry{Edmonds-Karp, SML}
      \addlegendentry{FIFO push-relabel, SML}
      \addlegendentry{Edmonds-Karp, Java}
      \addlegendentry{FIFO push-relabel, C++}
      \addlegendentry{FIFO push-relabel, C}
    % end legend information

@@

		  \addplot+[dashed, every mark/.append style={solid, fill=gray},mark=*] table {
		    1000 .024   
		    1500 .054   
		    2000 .103  
		    2500 .399  
		    3000 .719  
		    3500 1.362 
		    4000 2.036 
		    4500 3.334 
		    5000 4.785 
		    5500 6.079     
		  }; %Sparse, Edka, Java

@@

		  \addplot+[dashed, every mark/.append style={solid, fill=gray},mark=*] table {
		    1000	3.982
		    1050	4.463
		    1100	5.278
		    1150	6.27
		    1200	6.939
		    1250	7.953
		    1300	9.392
		    1350	10.317
		    1400	14.71
		    1450	13.11  
		  }; %Dense, Edka, Java

@@

    \node at (group c1r3.east) [anchor=west, xshift= 1.1cm] {\ref{grouplegend}};
  \end{tikzpicture}
\end{center}
\caption{Benchmark of different implementations. The x-axis shows the number of nodes, the y axis the execution time in seconds.}\label{fig:benchmark}
\end{figure}
